Study of the numerical solution of X-Modes equations around the hybrid resonnance

### 2015-01-20 report/intro.tex
\sqrt{alpha}-> lambda + remark about \sqrt{\alpha) and antennas in intro.tex
bug fix
minor changes #3
small fixes
intro draft

We consider the set of Maxwell equations with a linear current in two dimensions \cite{stable_yee_plasma_current}
 with absorption terms
 \begin{align*}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{align*}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions 
\begin{align*}
 H|_{-L}=g(t).
\end{align*}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \sqrt{\alpha(-{ L})}\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \sqrt{\alpha(-{ L})}\E_{inc} \wedge \n,
\ee
where  $\E_{inc} = \exp \left(\imath \sqrt{\alpha(-L)}x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$

$curl \E = 0$ at the right boundary

>>>>

 In the case of heating devices for fusion experiment, for example, one can find itself dealing with what is called hybrid resonnance. Hybrid resonnance may cause Maxwell's equation with strong magnetic fields to develop singular solutions \textcolor{red}{insert refs}. The energy deposit is resonant and may exceed by far the energy exchange which occurs in Landau damping \textcolor{red}{ref}. Contrary to the Landau Dumping, however, hybrid resonnance appears in a simpler model coupling fluid equations with the non electrostatic part of Maxwell equations.
 As it can be found in \cite{stable_yee_plasma_current}, we consider the non-stationary Maxwell system  
 \begin{align}
 -\varepsilon_0 \partial_t \E + \curl\, \Hbf = \J\\
 \mu_0 \partial_t \Hbf + \curl\,  \E = 0
 \end{align}
 coupled with a linear current in two dimensions $\J = -eN_e \ubf_e$

 \[
 m_e \partial_t \ubf_e =-e (\E +\ubf_e \nabla B_0).
 \]
 Here the unknows are the electromagnetc field $(\E,\Hbf)$ with the usual notation $\Hbf = \B/\mu_0$, $\J$ is the electronic current. We denote by $e$ the absolute value of the charge of elevtrons, 
  \begin{align*}
\epsilon_0\partial_t E_{x}-\partial_y H=-eN_e u_x,\\
\epsilon_0\partial_t E_{y}+\partial_x H=-eN_e u_y,\\
\mu_0\partial_t H+\partial_x E_y-\partial_y E_x=0,\\
m_e\partial_t u_x=eE_x+eu_yB_0-\nu m_e u_x,\\
m_e\partial_t u_y=eE_y-eu_xB_0-\nu m_e u_y
\end{align*}
posed in $[-L,\; \mathbb{R}]\times \mathbb{R}$. The boundary conditions 
\begin{align*}
 H|_{-L}=g(t).
\end{align*}

\textcolor{red}{!!!!!!maybe move this next part to later!!!!!!!!}
\subsection{Boundary condition}
Robin Boundary condition at the left boundary of the domain
\be
-curl \E -\imath \lambda\E \wedge \n = g_{inc} = -curl \E_{inc} -\imath \lambda\E_{inc} \wedge \n,
\ee
where  $\E_{inc} = \exp \left(\imath \lambda x\right)\begin{pmatrix} E_1\\ E_2 \end{pmatrix}$

$curl \E = 0$ at the right boundary
\begin{remark}
When modelling antennas in plasma physics, in such applications as ITER, a good choice of boundary condition could be the use of $\lambda = \sqrt{alpha(-L)}$
\end{remark}
\textcolor{red}{!!!!!!!!!!!!}
